Inference methods comparison for the simplified Naomi model

### 2023-03-07 src/naomi-simple_compare/comparison.Rmd
Work on getting samples of model outputs aligned with mf_out

These are the outcome variables which we might be interested in to monitor:

```{r}
names(tmb$fit$sample)[!(names(tmb$fit$sample) %in% pars)]
#' To-do: elicit from Jeff in particular which of these we should be focusing on the posterior output of
#' Guess would be the indicators HIV prevalence (rho_t1_out), ART coverage (alpha_t1_out), HIV incidence (lambda_t1_out)
```
# KS plots

>>>>

These are all of the outcome variables which we might be interested in to monitor:

```{r}
names(tmb$fit$sample)[!(names(tmb$fit$sample) %in% pars)]
```
The most important ones (checked with Jeff) are HIV prevalence (`rho_t1_out`), ART coverage (`alpha_t1_out`), and HIV incidence (`lambda_t1_out`).

* HIV prevalence has `r dim(tmb$fit$sample$rho_t1_out)[1]` variables (rows)
* ART coverage has `r dim(tmb$fit$sample$alpha_t1_out)[1]` variables (rows)
* HIV incidence has `r dim(tmb$fit$sample$lambda_t1_out)[1]` variables (rows)

```{r}
dim(tmb$fit$sample$rho_t1_out)
dim(tmb$fit$sample$alpha_t1_out)
dim(tmb$fit$sample$lambda_t1_out)
```

Within `tmb$naomi_data` there is a dataframe called `mf_out` (modelframe output) which contains the area, age, sex mapping these `r dim(tmb$fit$sample$rho_t1_out)[1]` rows.
As a sanity check, confirm that the number of areas times number of ages times number of sexes indeed equals the number of rows:

```{r}
mf_out <- tmb$naomi_data$mf_out
(n_area <- length(unique(mf_out$area_id)))
(n_age <- length(unique(mf_out$age_group)))
(n_sex <- length(unique(mf_out$sex)))

stopifnot(n_area * n_age * n_sex == dim(tmb$fit$sample$rho_t1_out)[1])
```

It makes sense only to assess inferential accuracy at the finest level so as to avoid double counting.

```{r}
mf_out$area_id %>% unique()
mf_out$sex %>% unique()
mf_out$age_group %>% unique()

mf_out %>%
  filter(
    area_id %in% paste0("MWI_4_", 1:32, "_demo"),
    sex %in% c("male", "female"),
    age_group %in%
      c(
        "Y000_004", "Y005_009", "Y010_014", "Y015_019", "Y020_024", "Y025_029",
        "Y025_034", "Y030_034", "Y035_039", "Y040_044", "Y045_049", "Y050_054",
        "Y055_059", "Y060_064", "Y065_069", "Y070_074", "Y075_079", "Y080_999"
      )
  ) %>%
  nrow()
```

# KS plots
